Individual heterogeneity in the functional topography of the medial prefrontal cortex

### 2019-03-13 Manuscript.Rmd
most of Joe's first pass of comments addressed

# Whether to apply subject-wise thresholds on maps or not
threshMaps <- TRUE

@@

## tanh-z transformation (variance stabilizing Fisher) and p-values (adjusted and not)
# This takes either a matrix of correlation values (vectors too, but manually compute pvals)
# Normalization approach suggested in network textbook (equation 7.10)
fisherTanh <- function(Data = padjMatrix){

@@

  # p-vals
  if (is.matrix(Data)) {
    z.vec <- transformed$tanhZ[upper.tri(transformed$tanhZ)]
    n <- dim(Data)[1]
  } else if (is.vector(Data)) {
    z.vec <- transformed$tanhZ
    n <- length(Data)
  }
  transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n-3)), lower.tail=F)

@@

      # had to place dashes on each side because grep grabbed strings containing the names (i.e. 47m, a24pr)
      #ROIS <- c("_7m_", vmPFC_labels) # c("_a24_", "_7m_")
      for (ROI in ROIS) {
        indx <- c(indx, grep(ROI, rownames(Data)))  
      }

@@

@@

  There is extensive topographic overlap between cortical regions associated with the default-mode network (DMN) and regions that exhibit effects of subjective value during decision making. The two sets of functional effects involve common regions of medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC). At the same time, differences between the two sets of activation patterns are apparent at the aggregated meta-analytic level, and further individual-level functional subdivisions might be obscured by group averaging. Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was preferentially implicated in DMN effects. We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to divide mPFC/PCC into distinct cortical communities in individual participants (n=100 from the Human Connectome Project). We labeled the communities "DMN" and "non-DMN" on the basis of their overlap with the meta-analytically identified PCC region. The spectral partitioning algorithm efficiently identified individual-level cortical subdivisions that were reliable over time and across test-retest days using moderate amounts of fMRI data (30 min per day). The topography of the identified subdivisions differed across individuals, and the degree of inter-individual variability was greater in mPFC than in PCC. Our results will aid future task-based fMRI studies in identifying functionally specific cortical subdivisions, and suggest it would be premature to infer that different task manipulations call upon shared cognitive processes solely because they evoke overlapping activation in mPFC at the group or meta-analytic level.

@@

  [i'm here] As such, there is value in examining all possible sources of covariation that compose DMN. Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017]. A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics [@Bassett2018a]. From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures [@Garcia2017]. Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network [@Fortunato2016]. Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups [@Garcia2017]. However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning (SP) a more valuable option. In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix). The resulting eigenvector corresponding to the second-lowest eigenvalue (i.e. the Fiedler vector) provides values to divide the network into a positive and a negative community [@Fiedler1975; @Belkin2003]. SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018]. This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.

  In this study, we aimed to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals. We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data. First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas [@Glasser2016]. We then produce a rsFC networks of all the surface vertices within these ROIs for each of 100 individual resting state dataset from the Human Connectome Project (HCP)[@VanEssen2012], and estimate the extent of DMN coverage through spectral partitioning. Our results suggest the intrinsic functional topography of mPFC and PCC can be reliably partitioned into at least two idiosyncratically arranged networks that can be obscured when averaged across subjects. These sub-networks resembled an organizational scheme recently observed in a handful of subjects (Braga & Buckner, 2017). We also show that graph theoretic tools are capable of identifying these sub-networks in isolated individuals. Our work highlights the usefulness of estimating brain effects at the individual level in these regions, and points to limitations of aggregative methods in determining the degree of neural overlap between DMN and valuation.

@@

@@

We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation [@Bartra2013] (n = 27 studies) and DMN [@Laird2009] (n = 77). These represent the surviving areas post-statistical thresholding from each study. For each study, each peak volumetric coordinate was mapped onto a 1mm standard space (MNI152) using AFNI's 3dcalc (CITATION). We then generated 10mm speheres at these points with FSL's fslmaths (CITATION), and then projected to a standard cortical mesh (fs_average, 32,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf (CITATION). The sphere sections that overlapped with the cortex were mapped to an atlas of the human cortical surface (360 regions)[@Glasser2016]. This produced a list of standardized parcels that were reported on each study.

<!-- 
With these lists, we identified the areas that were more consistently shared between DMN and valuation. For each literature, we summed the number of times each parcel was reported across studies, and performed a one-way chi-squared test of proportions on each parcel with a null probability equivalent to the bootstrapped (5000 iterations) mean of each literature's report counts. In other words, we checked which regions were significantly (p < 0.05) more reported in their respective literatures than their counterparts. Regions of interest were then determined based on which of the remaining regions were common across literatures.
-->

With these lists, we identified areas that were significantly more associated to either literature. We limited the search space to the parcels that were contained within the medial portion of the DMN parcellation defined by Yeo et al. [-@Yeo2011], as it broadly encompassed our a priori domain of interest (25 parcels across hemispheres). We permuted the label of every study (i.e. DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic from chi-squared tests of proportions that compared the number of studies that contained each area. This gave us a null distribution of 5000 chi-squared values. We then used the 95th percentile of this distribution as a significance threshold to evaluate the chi-squared values produced by comparing the actual rates of reporting of each area between literatures. The resulting ROIs contained two spatially discontiguous regions (Figure 1), which we label PCC and mPFC for further analyses.

@@

In order to quantify the resting connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects). Each subject's data was acquired over two days at Washington University in St. Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany). Four resting state sessions (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) were each comprised of 1200 TRs for a total scan time of 14 min 33 s, with left-right and left-right phase encoding implemented on each day. We used this scanning structure to estimate each subject's topology based on session, day, and overall data (4800 TRs).

Beyond the in-house minimally preprocessed pipeline from HCP [@Glasser2013], which includes considerable motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152-based normalization, all scans went through a number of additional refinements [@Tobyne2017]. These included band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), as well as mean greyordinate signal regression [@Burgess2016]. Only subjects with both left-right and right-left phase encoding were included (i.e. subjects with four rsfMRI sessions). In addition, only datasets with either low motion levels (under 1.5mm) or under 0.5 mm mean framewise displacement (FD) were used. Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses. Finally, data acquired on the same day (i.e. left-right and right-left phase encoding session) were temporally demeaned. Each subject's brain was comprised of 32k vertices per hemisphere. We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.

@@

All network analyses were performed using the igraph package (CITE) in R 3.4.1. To establish each subject's network, we selected all the vertices contained within the ROIs (n = 4,801 per subject) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them. Next, we applied Fisher's r to z transformation, and took the exponential of these values so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05). As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately (1200 TRs each); 2) the concatenated timeseries from each pair of daily sessions (2400 TRs total); 3) each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).

@@

Communities (i.e. clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2003]. First, each network was represented as an $n$ x $n$ matrix of previously adjusted correlation values (where $n$ = number of vertices within the ROIs, 4,801). This matrix was then transformed into its normalized Laplacian form

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlation values with every other vertex), and $W$ is the adjusted correlation matrix. This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. This transormation ensures that every row adds up to zero. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (from now on called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975]. Every individual map is therefore binarized by sign in order to evaluate the topography of each sub-network (see next section for details). Given that this data-driven method is agnostic to the prevalent function of each community (i.e. DMN or not DMN), we defined the DMN community to be the one containing the DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects). Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].

In order to evaluate the validity of the resulting partitions, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al. [-@Clauset2004]. This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network. The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity. Thus, unlike SP, modularity can fractionate a network into many functional groups. We assumed that if the partitions from the bounded and unbounded community detection methods show high level of agreement, we could gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.

@@

In order to evaluate the stability and topographical heterogeneity of the partitions within and across subjects, we chose the adjusted rand index (ARI) as the reference metric of agreement between two clusterings [@Hubert1985]. ARI estimates the rate at which every pair of nodes in partition A were jointly assigned to the same/different parcels on partition B, over all possible changes (e.g. clustered together on A, but separately on B). Therefore, the adjusted rand index determines the percentage of agreement between any two partitions while being agnostic to the labeling scheme. The resulting ratio is compared to a baseline given by the expectation of a random node assignment across partitions. This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index falls below chance).

We performed a number of comparisons among partitions. First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns. Modularity and SP show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018]. Their alignment would thus give us confidence in the validity of the resulting topologies. Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean ARI for the group. We then performed the same evaluation for PCC and mPFC separately, and examined whether there are mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise RI comparisons across subjects. Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we performed all the subsequent analyses on PCC and mPFC separately.

To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the clustering derived from the whole subject's data. The length of the windows is well equipped to find stable community features in brain networks [@Gordon2017]. In addition, given the high degree of overlap across adjacent windows, we attribute a vertex's tendency to persistently shift allegiances to noise. In that regard, and consdiering the descriptive relevance of Fiedler eigenvector values in previous fMRI research [@Tian2018], we also examined the relationship between the magnitude of Fiedler vector values with the proportion of times a vertex was part of the DMN community across windows. To do this, we performed a mixed effects logistic regression model, with subject as a mixed effect and vertex-wise eigenmap values (derived from their full dataset) as fixed predictors on the proportion of times each vertex participated in the DMN community. Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time (all other values were turned into zeros). Individuals without such stable nodes were not thresholded, but their maps were not discarded. Values in the eigenvector maps that did not meet threshold were set to zero, and set to 0.5 during binarization so that they would not bias the mean estimates across subjects. These thresholds yielded individual maps that retained the most stable vertices for further analyses, as well as discarding large sources of noise.

We then estimated the level of agreement between scans taken across days (i.e. pairs of daily left-right and right-left phase encoding sessions). If the functional organization estimated by SP is indeed subject-specific, we should see higher agreement for the same subject across days than either day compared to every other subject. We tested this idea by computing the ratio of the mean RI within and between subjects. Ratios close to one denoted good alignment across subjects, while ratios significantly higher than one suggested that partitions within a subject were more stable than what you would expect against every other subject. We then extend this idea by computing the overall agreement across all sessions. Similar to the day-to-day analysis, we expect that sessions within subjects would show higher agreement than between subjects. Given what we know about these general regions, we expected PCC to be fairly well aligned across participants, and stable within subjects. On the other hand, we hypothesized low agreement of mPFC partitions across participants, but with considerable stability across days and sessions within subject.

### *Estimation of Noise Effects*

@@

Next, we examined whether a vertex's affiliation to the DMN community was driven by its tSNR. First, we computed the mean time series of each subject's DMN community. We then performed a mass univariate analysis to predict the average time series from each individual vertice's time series. The resulting $R^2$ values from each model were extracted to determine the total variance of the mean DMN time series explained by each individual vertex. If high noise in more ventral mPFC areas is affecting our results, we should see a gradient of $R^2$ values that decreases ventrally across subjects. We then spatially correlated (Pearson) each subject's $R^2$ and tSNR values to determine whether low tSNR negatively impacted the individual contribution among vertices, and report the mean correlation across subjects.

@@

A potential downfall of our approach lies in whether the considerable computational demands are indeed required to identify these individualized partitions. It is possible that regional seed-based functional connectivity could provide sufficiently stable approximations of an individual's DMN arrangement. Given the high variability and idiosyncrasy of mPFC (see Results), we examined if SP could capture more reliable maps than seed-based functional connectivity in this area. First, we estimated each subject's DMN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average PCC activity for each day separately. We compared these seed-based maps with the Fiedler vectors produced by SP by spatially correlating them across days and subjects in three ways: 1) between seed-based maps; 2) between community-based maps; and 3) between correlation- and community-based maps. These spatial correlations were aimed to determine the day-to-day stability of each approach, as well as the overall level of agreement between them. These methods should produce somewhat similar arrangements, but the one displaying the highest within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Mueller2013a]). We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).

@@

<!--
### *Table 1. (UPDATE) Significant brain regions per literature*
| Literature                  | Significant Brain Regions   |
| :-------------------------- | --------------------------: |
| Default Mode Network        | `r paste(dmnLbls)`          |
| Subjective Value            | `r paste(valLbls)`          |
-->

>>>>

# general options
threshMaps <- TRUE # Whether to apply subject-wise thresholds on maps or not
feedback <- FALSE # show permutation progress?

@@

## tanh-z transformation (variance stabilizing Fisher) and p-values (adjusted and not)
# This takes either a matrix of correlation values (vectors too, but manually compute pvals)
# Normalization approach suggested in network textbook (equation 7.20)
# This transformation is approximately normal with mean 0 and sd = sqrt(1 / (n - 3))
fisherTanh <- function(Data = padjMatrix){

@@

  # p-vals
  if (is.matrix(Data)) {
    z.vec <- transformed$tanhZ[upper.tri(transformed$tanhZ)]
    n <- dim(Data)[1]
  } else if (is.vector(Data)) {
    z.vec <- transformed$tanhZ
    n <- length(Data)
  }
  transformed$pvals <- 2 * pnorm(abs(z.vec), 0 , sqrt(1 / (n - 3)), lower.tail = F) # no lower tail, but absolute Zs = two tailed

@@

      # had to place dashes on each side because grep grabbed strings containing the names (i.e. 47m, a24pr)
      for (ROI in ROIS) {
        indx <- c(indx, grep(ROI, rownames(Data)))  
      }

@@

      # Exponentiate to preserve distribution while ensuring positive weights
      # I'm keeping corrMat and transfMat$tanhZ separate in case I want to uncorrect transfMat in the future
      corrMat <- exp(corrMat)
      corrMat[corrMat == 1] <- 0
      transfMat$tanhZ <- corrMat

@@

  There is extensive topographic overlap between cortical regions associated with the default-mode network (DMN) and regions that exhibit effects of subjective value during decision making. The two sets of functional effects involve common regions of medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC). At the same time, differences between the two sets of activation patterns are not apparent at the aggregated meta-analytic level, and further individual-level functional subdivisions might be obscured by group averaging. Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was preferentially implicated in DMN effects. We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to divide mPFC/PCC into distinct cortical communities in individual participants (n=100 from the Human Connectome Project). We labeled the communities "DMN" and "non-DMN" on the basis of their overlap with the meta-analytically identified PCC region. The spectral partitioning algorithm efficiently identified individual-level cortical subdivisions that were reliable over time and across test-retest days using moderate amounts of fMRI data (30 min per day). The topography of the identified subdivisions differed across individuals, and the degree of inter-individual variability was greater in mPFC than in PCC. Our results will aid future task-based fMRI studies in identifying functionally specific cortical subdivisions, and suggest it would be premature to infer that different task manipulations call upon shared cognitive processes solely because they evoke overlapping activation in mPFC at the group or meta-analytic level.

@@

  Interrogating all sources of covariation through functional connectivity provides an avenue for capturing subject-specific brain organization. Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017]. A popular approach to analyze these connectomes is to rely on graph theoretic methods, which are properly equiped to understand brain network dynamics [@Bassett2018a]. From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures [@Garcia2017]. Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network [@Fortunato2016]. Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups [@Garcia2017]. However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes a forced dissection through spectral partitioning (SP) a more valuable option [@Fiedler1975; @Belkin2003]. SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018]. This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.

  In this study, we aimed to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals. We did this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain networks. First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that considerably overlapped with previously-defined DMN and limbic networks along the medial wall [@Yeo2011]. A meta-analysis of DMN and SV literatures revealed areas in PCC and mPFC that were uniquely related to DMN and SV, respectively (these areas were used as markers to identify the affiliation of each individual's communities). We then produced rsFC networks of all the surface vertices within these regions of interest (ROI) for each of 100 individual resting state dataset from the Human Connectome Project (HCP)[@VanEssen2012], and estimated the extent of DMN coverage through spectral partitioning. We found that these areas of overlap can be partitioned into two communities that topographically vary across subjects, but that follow a comon organizational principle. This partition was in substantial agreement with results from a different community detection algorithm (moularity). A sliding window analysis revealed that spectral partitioning allows for a more immediate identification of noisy viertices with unreliable affiliation. Refining the partitions by filtering out these nodes resulted in idiosyncratic partitions that were highly stable across scanning runs per individual, and this pattern was higher for mPFC. We show that partitions produced by spectral partitioning had higher test-retest reliability per subject than common seed-based functional connectivity, without the need of group-drived priors [@Kong2018]. Lastly, we provide evidence that these communities resembled an organizational scheme recently observed in a handful of subjects [@Braga2017]. Our work highlights the usefulness of estimating brain effects at the individual level in these regions, and points to limitations of aggregative methods in determining the degree of neural overlap between DMN and valuation.

@@

### *Search space*

For all our analyses, we defined our search space based on the 17 network parcellation proposed by Yeo et al. [-@Yeo2011]. First, Ww selected vertices on the cortical surface that were contained by the DMN and limbic networks along the medial wall. Next, we overlayed these networks on a parcellated atlas of the human cortical surface (360 regions) [@Glasser2016], and retained parcels that shared at least 15% of vertices with them. This resulted in 45 regions of interest (ROI) across hemispheres (Table 1). These ROIs were naturally divided into two spatially discontiguous clusters that covered PCC and mPFC, thus facilitating the study of each general region separately.

@@

We used a novel approach to cortical surface parcel-based meta-analysis to assess whether individual parcels were differentially associated with valuation or DMN effects. For subjective value, we gathered peak brain coordinates of activity from 198 studies that were associated with positive effects for current or prospective rewards [@Bartra2013]. For DMN, we acquired coordinates from a previous meta-analysis of 80 studies that were related to task-deactivation [@Laird2009]. These represent the surviving areas post-statistical thresholding from each study. For each study, we created an indicator map in standard space (MNI152, 1 mm resolution) which contained values of 1 in a 10 mm radius sphere around each reported activation peak, and values of 0 elsewhere[@Wager2009]. The indicator map for each study was then projected to a standard cortical mesh (fs_average, 32,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf [@Fischl2012] (http://surfer.nmr.mgh.harvard.edu/). Any sphere sections that overlapped with the cortex were mapped to our ROIs, and we tallied how many studies had positive indicator values in each parcel.

With these lists, we identified areas that were significantly more associated to either literature. We permuted the label of every study (i.e. DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic (across all parcels) from chi-squared tests of proportions that compared the number of studies that contained each area. This gave us a null distribution of 5000 chi-squared values. The 95th percentile of this distribution served as an FWE-corrected significance threshold to evaluate unpermuted chi-squared values.

@@

Oue fMRI analyses used resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects). Each subject's data was acquired over two days at Washington University in St. Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany). Four resting state runs (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) each comprised 1200 time points(14 min 33 s) for a totalof 4800 time points. Two runs were acquired on each day, with the phase encoding direction set to left-right for one run and right-left for the other. Only subjects with both left-right and right-left phase encoding were included (i.e. subjects with four rsfMRI sessions). In addition, only datasets with either low motion levels (under 1.5mm) or under 0.5 mm mean framewise displacement (FD) were used.

Data initially underwent the HCP minimally preprocessing pipeline [@Glasser2013], which included considerable gradient nonlinearity correction, motion correction, EPI distortion correction, temporal denoising based on independent components (FIX, [@Griffanti2014; @Salimi-Khorshidi2014]), high-pass filtering (0.0005 Hz threshold), and MNI152-based normalization. Data were further preprocessed using an in-house pipeline described previously [@Tobyne2017]. Steps included linear interpolation across timepoints with over 0.5 mm of framewise displacement, band-pass filtering (allowed frequencies ranged from 0.009 and 0.08 Hz), temporal denoising and high-motion censoring by deletion, as well as mean greyordinate signal regression [@Burgess2016]. Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses. Finally, data acquired on the same day (i.e. left-right and right-left phase encoding session) were temporally demeaned. Each subject's brain was comprised of 32k standard HCP greyordinates per hemisphere (combined in a CIFTI file). We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject.

@@

All network analyses were performed using the igraph package [@Csardi2006] in R 3.4.1 [@R Development Core Team]. To establish each subject's network, we selected all the vertices contained within the ROIs (n = 4,801 per subject) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them. Next, we applied Fisher's r to z transformation, and performed a two-sided significance test to identify strong correlations. The resulting p-values were corrected for multiple comparisons (FDR < 0.05), and edges with non-significant correlations were turned to 0 (all other edges retained their respective z-values). Next, we took the exponential of these values so that all weights were positive while maintaining the ordinal ranks of the original correlation distribution. Values of 1 of this transformed distribution were returned to 0 in order to avoid the inclusion of these edges in the network analyses. We report the proportion of retained edges (i.e. network density) in the Results section. As part of the evaluation step, we produced these network weight matrices (and the community detection outlined below) at four levels: 1) for each run separately (1200 TRs each); 2) for the concatenated time series for the two runs on the same day (2400 TRs total); 3) for each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).

@@

Communities (i.e. clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2003]. First, each network was represented as an $n$ x $n$ network weight matrix (where $n$ = number of vertices within the ROIs, 4,801). This matrix was then transformed into its normalized Laplacian form

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlation values with every other vertex), and $W$ is the network weight matrix. This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. This transformation ensures that every row adds up to zero. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (traditionally called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with [@Fiedler1975]. This method enforces the partition of a network into similarly-sized communities, and guarantees that they share at least one edge [@Chung1999]. In this way, spectral partitioning avoids producing communities that are too small to be physiologically meaningful (for example, isolated vertices that are considerably affected by measurement noise). Every individual partition is therefore binarized by sign in order to evaluate the topography of each community (see next section for details). Given that this data-driven method does not label the two communities or establish correspondence across participants, we defined each individual's "DMN" community to be the one containing the DMN-specific PCC parcel identified in our meta-analysis. Given the high density of these networks (see Results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].

In order to evaluate the convergent validity of the resulting partitions across community-detection methods, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al. [-@Clauset2004]. This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network. The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity. Unlike SP, modularity can fractionate a network into more than two functional groups. We assumed that if the partitions from the bounded and unbounded community detection methods showed high level of agreement, we could gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not. We also diagnose our choice of two communities by reporting the rank (from lowest to largest) of the first eigenvalue produced by spectral partitioning to be non-zero. This eigenvalue serves as an estimator of the optimal number of communities in a network [@Chung1999], such that a rank of two in our partitions justifies limiting the number of communities to two.

@@

In order to evaluate the stability and topographical heterogeneity of the communities within and across subjects, we chose the adjusted rand index (ARI) as the reference metric of agreement between two clusterings [@Hubert1985]. The base of the ARI is computed by the formula

$$\frac{a + b}{a + b + c + d}$$

Where $a$ is the number of pairs of nodes that were grouped together in both partitions, $b$ is the number that were grouped separately, and $c$ and $d$ denote the number grouped together (separately) in one partition, but separately (together) in the other. Therefore, ARI estimates the ratio at which every pair of nodes in partition A were jointly assigned to the same/different parcels on partition B, over all possible relational changes. The resulting ratio is adjusted by comparing it to a baseline given by the expectation of a random node assignment across partitions. This means that even though clustering deviations are heavily penalized, positive ARI values compare favorably against chance clustering (and can take negative values if the index given by the formula above falls below 50%). In short, the ARI determines the chance-corrected percentage of agreement between any two partitions while being agnostic to the labeling scheme.

We performed a number of comparisons among partitions. First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns. Modularity and SP have been previously found to show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018]. Their alignment would thus give us confidence in the validity of the resulting topologies. Next, we compared the functional organization derived from the whole time series across subjects, and report the mean pairwise ARI for the group. We then performed the same evaluation for PCC and mPFC separately, and examined whether there are mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise ARI comparisons across subjects. Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we performed all the subsequent analyses on PCC and mPFC separately.

To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the partition derived from the whole subject's data. A 20-min window is typically adequate for identifying stable community features in brain networks [@Gordon2017]. We assessed whether the magnitude of the Fiedler vector value for a given vertex (for the full subject-level data set) was associated with the stability of that vertex’s sub-network assignment across time windows. To do this, we fit a mixed effects logistic regression model, in which the dependent variable was the proportion of times each vertex participated in the DMN community across windows, and the explanatory variables included a random effect of subject and a fixed effect of the Fiedler vector value for that vertex (derived from their full dataset). Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time. *Individuals without such stable nodes were not thresholded, but their maps were not discarded. Values in the eigenvector maps that did not meet threshold were set to zero, and set to 0.5 during binarization so that they would not bias the mean estimates across subjects. These thresholds yielded individual maps that retained the most stable vertices for further analyses, as well as discarding large sources of noise. (MANY NOTES: this can go into the results, and will need to add 1) % of subjects without stable nodes, and 2) the mean and range for the % of nodes that were stable.*

We then estimated the level of agreement between network partitions estimated using data from individual days (with 2 days per participant). If the functional organization estimated by SP is indeed subject-specific, we should see higher agreement within subject (test/re-test across days) than across subjects. We tested this idea by computing the ratio of the mean ARI within and between subjects. Ratios close to one denoted similar within-subject and across-subject alignment, whereas ratios considerably higher than one suggested that partitions were more similar within-subject than across subjects. We then extended this idea by computing the overall agreement across all runs (4 per subject) Similar to the day-based analysis, we assessed whether session-level data showed higher agreement within-subject than between subjects.

<!--
### *Estimation of Noise Effects*

@@

Next, we examined whether a vertex's affiliation to the DMN community was driven by its tSNR. First, we computed the mean time series of each subject's DMN community. We then performed a mass univariate analysis to predict the average time series from each individual vertice's time series. The resulting $R^2$ values from each model were extracted to determine the total variance of the mean DMN time series explained by each individual vertex. If high noise in more ventral mPFC areas is affecting our results, we should see a gradient of $R^2$ values that decreases ventrally across subjects. We then spatially correlated (Pearson) each subject's $R^2$ and tSNR values to determine whether low tSNR negatively impacted the individual contribution among vertices, and report the mean correlation across subjects. 
-->

@@

We evaluated the performance of the spectral partitioning algorithm in comparison to a simpler partitioning approach using seed-based functional connectivity. First, we estimated each subject's DMN partition in mPFC based on its vertex-wise functional correlation (Pearson) with the average PCC activity for each day separately. We compared these seed-based maps with the Fiedler vectors produced by SP by spatially correlating them across days and subjects in three ways: 1) between seed-based maps; 2) between SP-based maps; and 3) between seed- and SP-based maps. These spatial correlations were aimed to determine the test/re-test reliability of each approach, as well as the overall level of agreement between them. The two methods are expected to produce somewhat similar arrangements, but the one displaying the higher within-subject agreement across days should be preferred (for a discussion on the stability of functional networks see [@Kong2018; @Mueller2013a]). We thus compared the mean within-subject inter-day correlation coefficients of each method through a paired permutation analysis (5000 iterations).

@@

### *Table 1. Regions of interest from Glasser et al. (2016). Prefixes indicate hemispheric location (e.g. R = right).*
| Literature           | Significant Brain Regions                 |
| :------------------- | ----------------------------------------: |
| ROIs                 | `r print(str_remove(Yeo_labels, "_ROI"))` |
